Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-22 paper.tex
commit

\begin{algorithm}
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{relevant Web services $rws$}
 \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
 Map each relevant service to an index in the particle's position vector\;
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     $queue \leftarrow$ map service in a descending order by particle's position vector\;
     $WG \leftarrow$ $generateWeightedGraph$()\;
	 Calculate the $WG$ fitness value\;

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0. Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid,da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition. To compare the composition solution generated by our approach with QoS-aware approach. We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches. In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.

>>>>

\begin{algorithm}
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{relevant Web services $rws$}
 \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
 Map each relevant service to an index in the particle's position vector\;https://www.facebook.com/
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     $queue \leftarrow$ map service in a descending order by particle's position vector\;
     $WG \leftarrow$ $generateWeightedGraph$()\;
	 Calculate the $WG$ fitness value\;

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test for Comprehensive Quality Evaluation Mode and QoS Evaluation Model}\label{comparisonTest}
To analyse the differences between optimal solutions evaluated by comprehensive evaluation model and QoS evluation mode, We first look at the $MT$, $S$ and $QoS$

QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0. Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid,da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition. To compare the composition solution generated by our approach with QoS-aware approach. We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches. In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.
